Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
OpenStack ampliacion

From the HPC perspective, OpenStack offers high performance computing (HPC) configurations using
multiple supported hypervisors and different hardware architectures. However, despite to be able to
specify some extra parameters for special resources like GPUs, chooding a host based on the existence
of a GPU is currently unsupported in OpenStack \cite{OpenStackGPU}.

>>>>

From the HPC perspective, OpenStack offers high performance computing (HPC) configurations using
multiple supported hypervisors and different hardware architectures. However, despite to be able to
specify some extra parameters for special resources like GPUs, choosing a host based on the existence
of a GPU is currently unsupported in OpenStack \cite{OpenStackGPU}.
